\mychapter{3}{Article III: Directors}

\section{Rules and Requirements}
\begin{enumerate}
	\item The term of director is one academic year.
	\item No member may hold two positions simultaneously unless required by 3.2.3 of this Constitution.
	\item No member may be elected or appointed to the same position for three full consecutive terms unless there is no other qualified candidate.
	\item No more than three members may serve in Permanent Director Positions in their last year at UCSC unless there is no other qualified candidate.
	\item A member must serve on Board of Directors for a term before they can run for the positions of chairs.
	\item All directors serving in Permanent Director Positions must, upon election, become members of Association for Computing Machinery International.
\end{enumerate}

\section{Permanent Director Positions}
\begin{enumerate}
	\item ACM at UCSC shall have six permanent director positions:
	\begin{enumerate}
		\item Chair
		\item Vice Chair
		\item Secretary
		\item Treasurer
		\item Outreach Officer
		\item Webmaster
	\end{enumerate}
	\item A member may be elected to these positions according to the procedures specified in this Constitution.
	\item In case of one or more of Permanent Director Positions are not filled, The Board of Directors shall:
	\begin{enumerate}
		\item Transfer the duties of the unfilled position to another director before a member can be appointed or elected to fill that position.
		\item Appoint a member to the unfilled position with the recommendation of Chair and consent of a minimum of two-third of Board of Directors membership; Or, by the petition of a minimum of one-third of Board of Directors membership, commerce a special election according to the procedures specified in this Constitution to elect a member to the unfilled position.
	\end{enumerate}
\end{enumerate}

\section{New Director Positions}
\begin{enumerate}
	\item New Director Positions may be created with the consent of a minimum of two-third of Board of Directors membership.
	\item Titles of New Director Positions shall be specified in the Bylaws.
	\item A member may be appointed to these positions with the consent of a minimum of two-third of Board of Directors membership.
	\item A member may be elected to these positions according to the procedures specified in this Constitution.
	\item These positions shall be removed once they are vacated.
	\item No new director position may be created if one or more of Permanent Director Positions are not filled.
\end{enumerate}

\section{Emeritus Director Positions}
\begin{enumerate}
	\item Upon election, up to two directors of former Board of Directors may choose to retain in new Board as Emeritus Director.
	\item Emeritus Directors shall retain their titles but with "Emeritus" suffix.
	\item Former chairs shall get the priority. If they decline, former Board may vote to select Emeritus Director.
\end{enumerate}

\section{Board of Directors}
\begin{enumerate}
		\item Board of Directors shall consist of all directors.
		\item Board of Directors shall meet when called by Chair or when called by a minimum of one-third of Board of Directors membership.
		\item Faculty adviser, a designated representative of each SIG and a designated representative of each committee may attend the meeting unless one-third of directors object.
		\item Board of Directors, with the consent of two-third majority of its membership, may invite other people to the meeting.
		\item Board of Directors voting rights extend only to directors.
		\item Board of Directors shall have following duties shared by all directors:
		\begin{enumerate}
			\item Provides leadership and direction to ACM at UCSC;
			\item Understands and adheres to the Constitution of ACM at UCSC.
		\end{enumerate}
\end{enumerate}

\section{Duties of Directors}
\begin{enumerate}
	\item Chair
	\begin{enumerate}
		\item Presides at meetings of the Chapter and oversees the activities of the board;
		\item Coordinates Chapter activities with the board members;
		\item Establishes short- and long-range objectives and goals in conjunction with the board members;
		\item Structures the organization to ensure continuity of leadership by providing opportunities for new leaders to develop and to be mentored;
		\item Involves all ACM members in the local chapter by planning activities that appeal to a wide spectrum of interests;
		\item Approves all Chapter communications;
		\item Ensures the completion of the Chapter annual report each year.
	\end{enumerate}
	\item Vice Chair
	\begin{enumerate}
		\item Presides at meetings in the absence of the Chair;
		\item Plans, coordinates, and recruits to manage a series of meetings and programs and activities;
		\item Coordinates programs with the Chair and the board members;
		\item Provides data on previous Chapter events to allow the event Chair to benefit from past experience and suggestions for improvement;
		\item Provides timely and interesting advance information for newsletters, social media, and mailings;
		\item Provides or coordinates information on forthcoming events to the Secretary for inclusion in meeting notices or newsletters;
		\item Ensures strong leadership succession by identifying and recruiting new Chapter volunteers;
		\item Provides mentorship to new officer(s).
	\end{enumerate}
	\item Secretary
	\begin{enumerate}
		\item Handles the correspondence of the Chapter and keeps records of it;
		\item Maintains official records of meetings;
		\item Informs officers of deadlines for reports, mailings, future commitments;
		\item Organizes and oversees the elections according to the procedures specified in this Constitution;
		\item Works closely with Webmaster to maintain a roster of officers and other board members with current address, including email, and telephone information;
		\item Works closely with Outreach Officer to promote upcoming events and communicate with Chapter members;
		\item Assists Treasurer and Outreach Officer to prepare the documents for fundraising events;
		\item Maintains complete and up-to-date copies of the Chapter's paperwork and other organizational documents.
	\end{enumerate}
	\item Treasurer
	\begin{enumerate}
		\item Oversees Chapter finances, collects dues, and receives other monies, e.g. proceeds from fundraisers;
		\item Follows best financial practices in consolidation with the board members;
		\item Completes and submits the annual financial report;
		\item Assists the Chair and other officers in preparing program budgets and financial controls;
		\item Coordinates activities and fundraisers with the board;
		\item Maintains and supervises Chapter bank accounts;
		\item Ensures that adequate budget and financial controls are maintained;
		\item Prepares and submits financial statements to the Chair and the board on a regular basis, i.e. all board meetings or at minimum quarterly;
		\item Works closely with Outreach Officer to organize and oversee the fundraising events of the Chapter;
		\item Pays all Chapter bills on time.
	\end{enumerate}
	\item Outreach Officer
	\begin{enumerate}
		\item Collaborates with other members of the board to create and execute exciting, interesting events for the Chapter constituency, e.g. Company Tours, professional events;
		\item Works closely with Treasurer to ensures the fiscal viability of all events;
		\item Works closely with Treasurer to organize and oversee the fundraising events of the Chapter;
		\item Works closely with Secretary to promote upcoming events and maintain records of correspondence;
		\item Gives alerts of upcoming events with details so the event may be advertised and marketed well;
		\item Publicizes Chapter activities through email, social media and the Chapter website.
	\end{enumerate}
	\item Webmaster
	\begin{enumerate}
		\item Keeps the organization’s website up to date;
		\item Maintains Chapter history and list of past officers;
		\item Updates meeting time and location information on the website;
		\item Create/maintain website from that allows for new members to join the mailing list;
		\item Generates ideas regarding content and applies appropriate member ideas.
		\item Coordinates mailing of notices/newsletters to members and alumni;
		\item Works closely with Secretary and Outreach Officer to inform Chapter members of plans and activities by forwarding copies of all mailings and special reports;
		\item Works in coordination with BSOE webmaster to add any edits to the ACM website and/or give other and incoming board members access to edit webpage.
	\end{enumerate}
	\item New Director Positions
	\begin{enumerate}
		\item Duties of New Director Positions shall be specified in the Bylaws.
		\item Chair, with the advice and consent of a minimum of two-third of Board of Directors membership, may delegate duties of one or more Permanent Director Positions to New Director Positions.
	\end{enumerate}
	\item Emeritus Director Positions
	\begin{enumerate}
		\item Emeritus Directors shall provide advice to Board of Directors.
		\item Emeritus Directors shall especially help directors who serve in former Board positions of Emeritus Directors.
	\end{enumerate}
\end{enumerate}

\newpage
